---
title: "MHTdiscrete Quick Start Guide"
author: "Yalin Zhu (yalin.zhu@outlook.com)"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{MHTdiscrete Quick Start Guide}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This vignette summarizes the functions in the `MHTdiscrete` package, and provides some examples to illustrates how to use the package.  

First of all, you need to install the R package.
```{r warning=FALSE, eval=FALSE}
install.packages("MHTdiscrete")
```
then attach it
```{r}
library(MHTdiscrete)
```

The clinical safety example in Zhu and Guo^[Zhu, Y., & Guo, W. (2018). Familywise Error Rate Controlling Procedures for Discrete Data. *arXiv preprint arXiv:1711.08147*.]:

```{r}
df <-  data.frame(X1=c(4, 2, 2, 13, 6, 8, 4, 0, 1), N1 = rep(148, 9),
                  X2 = c(0, 0, 1, 3, 2, 1, 2, 2, 2), N2 = rep(132, 9))
  # obtain the avaiable p-values and attainable p-values using two-sided Fisher's Exact Test
  
  # store the avaiable p-values
 (p <- getPval(raw.data=df, test.type = "FET",alternative = "two.sided")$available.pvalue)
  # store the attainable p-values
 (p.set <- getPval(raw.data=df, test.type = "FET",alternative = "two.sided")$attainable.pvalue)
```

Apply single-step testing procedures:

```{r}
library()
data.frame(df, Orig.p = p,
           Bonf.adjp = p.adjust(p, method = "bonferroni"),
           Sidak.adjp = Sidak.p.adjust(p),
           Tarone.adjp = Tarone.p.adjust(p, p.set),
           MBonf.adjp = MBonf.p.adjust(p, p.set)) %>% 
  datatable() %>%
  formatRound(c(5:9), 4) %>%
  formatStyle(c('Bonf.adjp', 'Sidak.adjp', 'Tarone.adjp', 'MBonf.adjp'),
              fontWeight = styleInterval(0.1, c('bold', 'normal')), 
              color = styleInterval(0.1, c('red', 'black')),
              backgroundColor = styleInterval(0.1, c('pink', '')))
```

Apply step-down testing procedures:


```{r}

data.frame(df, Orig.p = p,
           Holm.adjp = p.adjust(p, method = "holm"),
           TH.adjp = TH.p.adjust(p, p.set),
           MHolm.adjp = MHolm.p.adjust(p, p.set)) %>% 
  datatable() %>%
  formatRound(c(5:8), 4) %>%
  formatStyle(c('Holm.adjp', 'TH.adjp', 'MHolm.adjp'),
              fontWeight = styleInterval(0.1, c('bold', 'normal')), 
              color = styleInterval(0.1, c('red', 'black')),
              backgroundColor = styleInterval(0.1, c('pink', '')))
```

Apply step-up testing procedures:


```{r}

data.frame(df, Orig.p = p,
           Hochberg.adjp = p.adjust(p, method = "hochberg"),
           Roth.adjp = Roth.p.adjust(p, p.set),
           MHoch.adjp = MHoch.p.adjust(p, p.set)) %>% 
  datatable() %>%
  formatRound(c(5:8), 4) %>%
  formatStyle(c('Hochberg.adjp', 'Roth.adjp', 'MHoch.adjp'),
              fontWeight = styleInterval(0.1, c('bold', 'normal')), 
              color = styleInterval(0.1, c('red', 'black')),
              backgroundColor = styleInterval(0.1, c('pink', '')))
```

Vignettes are long form documentation commonly included in packages. Because they are part of the distribution of the package, they need to be as compact as possible. The `html_vignette` output type provides a custom style sheet (and tweaks some options) to ensure that the resulting html is as small as possible. The `html_vignette` format:

- Never uses retina figures
- Has a smaller default figure size
- Uses a custom CSS stylesheet instead of the default Twitter Bootstrap style

## Vignette Info

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
